These are the instructions:

```{r}
# Load other packages here.
if (!require("tidyverse")) install.packages("tidyverse"); library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)
if (!require("UsingR")) install.packages("UsingR"); library(UsingR)
if (!require("cowplot")) install.packages("cowplot"); library(cowplot)
if (!require("car")) install.packages("car"); library(car) # Anova function for better lm summary stats
if (!require("multcomp")) install.packages("multcomp"); library(multcomp) # glht function for Tukey test
if (!require("emmeans")) install.packages("emmeans"); library(emmeans) # emmeans and pairs functions for post-hoc analysis
if (!require("conflicted")) install.packages("conflicted"); library(conflicted) # For dealing with conflicts
if (!require("tidyverse")) install.packages("tidyverse"); library(tidyverse) # For everything
conflict_prefer_all("dplyr", quiet = TRUE)
library(ggplot2)
```


```{r}

Data <- read.csv("dinosaurus_dozen_clean.csv")
Data |> 
  group_by(dataset) |> 
  summarize(
      mean_x    = mean(x),
      mean_y    = mean(y),
      std_dev_x = sd(x),
      std_dev_y = sd(y),
      corr_x_y  = cor(x, y)
      )
```
First, we are going to visualize the data. We will start by making a box plot for "x" variables with the following code.
```{r}
Data |>
  ggplot(aes(x = x)) +
    geom_boxplot() +
    theme_void() +
    theme(legend.position = "none")
```

What are some issues with this boxplot?
1. All x values are plotted together instead of by dataset
2. No color

We can add color in the aes() function as seen below.
Additionally, we can split the boxplot up by dataset using facet_wrap().
```{r}
Data |>
  ggplot(aes(x = x, colour = dataset)) +
    geom_boxplot() +
    theme_void() +
    theme(legend.position = "none") +
    facet_wrap(~dataset, ncol = 3)
```

This looks much better and helps us visualize each individual dataset. Now create the same boxplots for the y variables.
```{r}
Data |>
  ggplot(aes(x = y, colour = dataset))+
    geom_boxplot()+
    theme_void()+
    theme(legend.position = "none")+
    facet_wrap(~dataset, ncol = 3)
```



```{r}
Data |> 
  ggplot() +
  aes(x = x, color = dataset, fill = dataset) +
  geom_histogram() +
  facet_wrap(~dataset)+
  theme_cowplot()
```

```{r}
Data |> 
  ggplot() +
  aes(x = y, color = dataset, fill = dataset) +
  geom_histogram() +
  facet_wrap(~dataset)+
  theme_cowplot()
```


```{r}
Data |> 
  ggplot() +
  aes(x = x,  fill = dataset) + 
  geom_density(alpha=.3) +
  facet_wrap(~dataset)
  theme_cowplot()
```

```{r}
Data |> 
  ggplot() +
  aes(x = y,  fill = dataset) + 
  geom_density(alpha=.3) +
  facet_wrap(~dataset)
  theme_cowplot()
```

```{r}
Data |> 
  ggplot(aes(x = x, y = y, colour = dataset))+
    geom_point()+
    theme_void()+
    theme(legend.position = "none")+
    facet_wrap(~dataset)
```

